---
title: "Steps to add new datasets"
author: "Edgar Ortiz Brizuela"
date: "2024-09-24"
output: html_document
editor_options: 
  chunk_output_type: console
---

Instructions modified from: https://rstudio4edu.github.io/rstudio4edu-book/data-pkg.html


1. Copy and paste the original dataset in the `data-raw` folder.
2. Open the `load_data.R` file in the `data-raw folder`
3. Write the code needed to read the new dataset.  

```{r}
# EXAMPLE:
# covidkenya<-read.csv("data-raw/covidkenya.csv")
```

4. Include the name of the dataset that was read in the usedata function in the same file.

```{r}
# EXAMPLE:
# use_data(anscombe_set1, overwrite = TRUE)
```

5. Run the `load_data.R` script and save it. A cleaned up .rda data file is now created in the folder called data/.
6. Verify all data sets made it in your package by loading the package (Build pane > Click More > Load All or in the console using devtools::load_all()). And then call your dataset (e.g., plato, it should be in the environment, not needed as data, it is just loaded)
7. In the RStudio Build pane > click the `Check` button. The only warning should be that we need documentation from the new dataset, we will add it in the next steps. Another option is to use in the console: devtools::check(document=FALSE)).
8. Document the dataset:7. Run in the console usethis::use_r() with your data set name in quotes, which will generate a new .R script that lives in an R/ folder.

```{r}
# EXAMPLE
# usethis::use_r("covidkenya")
```

9. In this new .R script, copy and paste the information from another R file (eg, covidkenya) in the same R/ folder and update the information accordingly. 
10. The menu is drafted but not yet accessible by the package. In the console, run devtools::document() to make the Roxygen comments “concrete”.
11. This generates a .Rd file, that makes our documentation accessible to the package. Our official documentation lives inside a newly-generated man/ folder. 
12. Confirm the code worked: 
```{r}
# EXAMPLE
# ?covidkenya
```

13. Now, open the DESCRIPTION file and update the version number.
14. Check again for any issue using devtools::check(document=FALSE)) in the console. 
15. Add the package documentation using the following code in the console (answer absolutely yes):

```{r}
usethis::use_package_doc()
usethis::use_tibble()
devtools::document()
```

16. Build and install the official package to make it official by running the following code:

```{r}
devtools::install()
```

17. Push everything to GitHub using GitHub desktop.
18. Anyone can now install your package with the following code, substituting the field in quotes with your own GitHub username and package name:

```{r}
# install.packages("remotes")
remotes::install_github("mcarabali1/epib.704.data")
```





















